\section{Eco-driving Advices}\label{ecodriving}
%Landevejen er 23 til 24 \% billigere end motorvejen
The authors of \cite{EcodrivingAdvice} and \cite{KorGront} list a number of advices for eco-driving that will reduce fuel consumption.
The advices are detailed below and will be evaluated in the follwing sections separately.  

\begin{enumerate}
\item \label{advice.highGearLowRPM} \textbf{Drive in the heigest possible gear at lowest possible rounds per minut (RPM's).}
Fuel consumption is lower at low RPM's due to internal friction. 
Keep a high load on the engine and shift gear at around 2,500 RPM for gasoline cars and 2,000 RPM for diesel cars. 
\item \label{advice.steadySpeed} \textbf{Maintain a steady speed.} 
Fuel is primarily consumed when accelerating.
Constantly breaking and accelerating will use more fuel than maintaining a steady speed.
It also has a positive influence on exhaust emissions, traffic safety and flow.
\item \label{advice.anticipateFlow}\textbf{Anticipate traffic flow and avoid frequent starts and stops.}
Adjusting the speed to traffic lights, turns and other vehicles in good time will make it easier to maintain a steady speed.
\item \label{advice.decelerate}\textbf{Decelerate smoothly.}
Slow down by using the engine brake or the neutral gear in-stead of the actual brakes. 
Modern vehicles use little to no fuel when using the engine brake, i.e. the vehicle is in gear and the accelerator is released. 
It also reduces wear and tear and reduce exhaust emmisions, increase traffic safety and flow.
\item \label{advice.accelerate}\textbf{Accelerate moderatly.}
Rapid acceleration especially at high speeds consumes much fuel, and one should accelerate at low gears.
\item \label{advice.idle}\textbf{Eliminate idling.}
It is more fuel efficient to switch off the engine than leaving the engine running.
The average modern vehicle use about 0.5 liters per hour ($l/h$) during idling.
\item \label{advice.speedLimit}\textbf{Drive at or below the speed limit.}
Fuel consumption increases at higher speeds.
\item \label{advice.startup}\textbf{Do not press the accelerator when switching on the engine.}
This is not neccesary in modern vehicles and only consumes fuel.
\item \label{advice.curves}\textbf{Approach curves at correct speed and in the highest possible gear.}
This will reduce the need for acceleration after the curve and improve traffic safety.
\item \label{advice.weightAir}\textbf{Minimise extra weight and air resistance.} 
Both increase the load on the engine and thereby increse fuel consumption.
\item \label{advice.tyre}\textbf{Maintain correct tyre pressure.}
Incorrect tyre pressure increases the rolling resistance and thereby the fuel consumption.
\item \label{advice.accessories}\textbf{Avoid fuel consumption accessories.}
Air-conditioning and other accesories consume fuel.
%\item \label{advice.devices}\textbf{Use fuel saving in-car devices.}
%Several devices will help to follow some of the rules above. 
%The revolution counter will show RPM, the cruise control will help to maintain a steady speed and on-board computers can give feedback on currect consumption.
\end{enumerate}


